---
title: "COVID-19 Response | Quilombola Community in Brasil"
output: 
  flexdashboard::flex_dashboard:
      theme: bootstrap
      orientation: columns
      vertical_layout: fill
---

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 100%}

body {
color: "#796e66";
background-color: black;
zoom: 98%;
}
</style>

<style>
  .originOffset {
    transform: translate(-1px, -1px);
  }
</style>





<!-- this is to get rid of the tile layer lines -->
<script>
  var pane1 = map.createPane('pane1');
  var pane2 = map.createPane('pane2');

  pane1.style.zIndex = 210;
  pane2.style.zIndex = 220;

  L.DomUtil.addClass(pane1, 'originOffset');

  var layer1 = L.tileLayer( ... , {
    pane: 'pane1',
    ...
  });
  var layer2 = L.tileLayer( ... , {
    pane: 'pane2,
    ...
  });
  var layer = L.layerGroup([layer1, layer2]);
</script>
<!-- this is to get rid of the tile layer lines -->


<!-- <script> -->
<!-- $('.navbar-logo').wrap('<a href="http://www.ndhealth.gov" target=_blank>'); -->
<!-- </script> -->

<!-- <script src="https://maps.googleapis.com/maps/api/js?key=AIzaSyD1n2y7MnhppQ0WeVkV2gs-Y9sFtEfSuVI" async defer></script> -->
<!-- <link rel="stylesheet" href="https://unpkg.com/leaflet@1.3.4/dist/leaflet.css" -->
<!--   integrity="sha512-puBpdR0798OZvTTbP4A8Ix/l+A4dHDD0DGqYW6RQ+9jxkRFclaxxQb/SJAWZfWAkuyeQUytO7+7N4QKrDh+drA==" -->
<!--   crossorigin=""/> -->


<!-- <script src="https://unpkg.com/leaflet@1.3.4/dist/leaflet.js" -->
<!--   integrity="sha512-nMMmRyTVoLYqjP9hrbed9S+FzjZHW5gY1TWCHA5ckwXZBadntCNs8kEqAWdrb9O7rxbCaA4lKTIWjDXZxflOcA==" -->
<!--   crossorigin=""></script> -->

<!-- <script src='https://unpkg.com/leaflet.gridlayer.googlemutant@latest/Leaflet.GoogleMutant.js'></script> -->





<!-- <script type="text/javascript" src="https://maps.googleapis.com/maps/api/js?key=AIzaSyD1n2y7MnhppQ0WeVkV2gs-Y9sFtEfSuVI"></script> -->

<!-- <script src="https://unpkg.com/leaflet@1.0.2/dist/leaflet.js"></script> -->
<!-- <link rel="stylesheet" href="https://unpkg.com/leaflet@1.0.2/dist/leaflet.css" /> -->




<!-- <script src="https://maps.googleapis.com/maps/api/js?key=AIzaSyD1n2y7MnhppQ0WeVkV2gs-Y9sFtEfSuVI" async defer></script> -->
<!-- <link rel="stylesheet" href="https://unpkg.com/leaflet@1.3.4/dist/leaflet.css" -->
<!--   integrity="sha512-puBpdR0798OZvTTbP4A8Ix/l+A4dHDD0DGqYW6RQ+9jxkRFclaxxQb/SJAWZfWAkuyeQUytO7+7N4QKrDh+drA==" -->
<!--   crossorigin=""/> -->
<!-- <script src="https://unpkg.com/leaflet@1.3.4/dist/leaflet.js" -->
<!--   integrity="sha512-nMMmRyTVoLYqjP9hrbed9S+FzjZHW5gY1TWCHA5ckwXZBadntCNs8kEqAWdrb9O7rxbCaA4lKTIWjDXZxflOcA==" -->
<!--   crossorigin=""></script> -->


``` {js}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```



```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)


##tasks:
#add clustering of cases
#add timeseries data on top right for case data
##see discrepencies between douglas app and html
##copy muryel for risk map
##
##
##



library(flexdashboard)
library(DT)
library(leaflet)
library(htmlwidgets)
library(jsonlite)
library(rjson)
library(htmltools)
library(htmlwidgets)
library(maptools)
library(RgoogleMaps)
library(raster)
library(geoR)
library(rgdal)
library(readr)
library(ggmap)
library(tidyverse)
library(readr)
library(rgeos)
library(RCurl)
library(googledrive)
library(googlesheets4)
library(plotly)
options(scipen = 999) #so numbers dont display as scientfic notation
register_google(key = "AIzaSyD1n2y7MnhppQ0WeVkV2gs-Y9sFtEfSuVI")

library(googlesheets4)
library(stringr)
options(tigris_use_cache = TRUE)
options(tigris_class = "sp")

gs4_auth()#takes you to authenicate your google account
##get error to Sign in with Google temporarily disabled for this app This app has not been verified yet by Google in order to use Google Sign In.
if (interactive()) {
  # load/refresh existing credentials, if available
  # otherwise, go to browser for authentication and authorization
  gs4_auth()
  
  # force use of a token associated with a specific email
  gs4_auth(email = "elnim002@umn.edu")
  
  # use a 'read only' scope, so it's impossible to edit or delete Sheets
  gs4_auth(
    scopes = "https://www.googleapis.com/auth/spreadsheets.readonly"
  )
  
  # use a service account token
  gs4_auth(path = "foofy-83ee9e7c9c48.json")
}

gs4_find() #finds all files in googlesheet
1
# get the UCLA Law COVID-19 google sheet
be <-gs4_find("Quilombola Dashboard Data") #finds all files in googlesheet
be

#convert to data.frame
data<-range_read(be$id, sheet =  "data", skip=0) %>% 
  data.frame()

1

setwd("~/Desktop/geohackathon")

# #shapefile country brasil & transformation
# brasil<-readOGR("BRA_adm0.shp") %>% ##read in shapefile; source Meline
#   spTransform(CRS("+proj=longlat +ellps=WGS84 +datum=WGS84")) ##transform shapefil to World Geodetic System 84 

##extracting brasil boundary from google drive
# be1 <- drive_get("bra_adm0.zip")
# temp<-tempfile(fileext="bra_adm0.zip")
# download.file("https://drive.google.com/file/d/1AYhxsczpY4yEp51DpNQRVRMbxwWW5acl/view?usp=sharing", temp) #file for brasil boundary
# dl <- drive_download(
#   as_id(be1$id), path = temp, overwrite = TRUE)
# # brasil <- unzip(temp, exdir = tempdir()) %>%
# #   cbind.data.frame(stringsAsFactors=F) %>% 
# #   filter(row_number()==12L) %>% 
# #   as.character() %>% 
# #   readOGR() %>% 
# #   spTransform(CRS("+proj=longlat +ellps=WGS84 +datum=WGS84")) ##transform shapefil to World Geodetic System 84 
# 


#shapefile quilombola community
# quil<-readOGR("Territ¢rios_Quilombolas.shp") %>% ##read in shapefile; source Meline
#   spTransform(CRS("+proj=longlat +ellps=WGS84 +datum=WGS84")) ##transform shapefil to World Geodetic System 84 

##extracting Quilombola boundary from google drive
be2 <- drive_get("Shapefile - Quilombola Territories in Oriximin _PA.zip")
temp2<-tempfile(fileext="Shapefile - Quilombola Territories in Oriximin _PA.zip")
download.file("https://drive.google.com/file/d/1DATIVRULYUyBG1mebYgiPKb3pg2AbPzv/view?usp=sharing", temp2) #file for brasil boundary
dl2 <- drive_download(
  as_id(be2$id), path = temp2, overwrite = TRUE)
quil <- unzip(temp2, exdir = tempdir()) %>%
  cbind.data.frame(stringsAsFactors=F) %>% 
  filter(row_number()==10L) %>% 
  as.character() %>% 
  readOGR() %>% 
  spTransform(CRS("+proj=longlat +ellps=WGS84 +datum=WGS84")) ##transform shapefil to World Geodetic System 84 





#csv data attributes with geography
# data<-read.csv("data.csv", stringsAsFactors = F) #csv with geography and other attributes 
datageo<-merge(quil, data, by.x="OBJECTID", by.y="OBJECTID",  stringsAsFactors = F) #joinining shp w/ data


# writeOGR(datageo, ".", "quilprjdata", driver="ESRI Shapefile")



#randomly selected points as facility locations
# rpts<-spsample(quil, n = 30, "random") %>% ##random points; should be later read.csv
#   spTransform(CRS("+proj=longlat +ellps=WGS84 +datum=WGS84"))  ##transform shapefile to World Geodetic System 84 
# rpts<-SpatialPointsDataFrame(data = data.frame(ID=1:30), 
#                              coords = as.data.frame(rpts@coords[,1:2]))
#csv facility information and location
# facgeo<-read.csv("facgeo.csv") #facilities csv
#convert to data.frame
facgeo<-range_read(be$id, sheet =  "facgeo", skip=0) %>% 
  data.frame()


#data attributes associated with centroid polygon for each community with coordinate info
cdata<-coordinates(gCentroid(datageo, byid = T)) %>% 
  cbind(datageo@data) %>% 
  data.frame(ID=1:9)

#coords of polygons centroid as spatial points
coords= coordinates(gCentroid(datageo, byid = T)) #centroid coords
cpts<-SpatialPointsDataFrame(cdata, coords=coords[,1:2])




#label centroid location of polygon
cntyinfo = paste(
  "<b>","Locality: ", "</b>", cdata$Nom.x,
  sep = "") %>%
  lapply(htmltools::HTML)

#label for the cases
caseslabel<-paste("<b>", "# of Cases Confirmed: ", "</b>" , as.character(cdata$totcases), " in ", cdata$Nom.x, " as of June 26, 4:02:47PM",
                  "</br>", "<b>" , "Infection Rate per Locality: ", "</b>" , round((cdata$totcases)/(cdata$totpop)*100,2) , " per pop", " (cases/locality pop)*00", sep = "") %>%
  lapply(htmltools::HTML)


#label for facilities
facinfo = paste(
  "<b>","Facility: ", "</b>", facgeo$Name.of.Facility.Google.Name,"<br>",
  "<b>","Facility Type: ", "</b>", facgeo$Facility.Type.Google,"<br>",  
  "<b>","Phone: ", "</b>", facgeo$Phone,"<br>",                
  
  "<u>","Current Numbers", "</u>", "<br>",
  
  "<b>","Patient Census: ", "</b>", facgeo$What.is.your.current.number.of..Patient.Census,"<br>",
  # "<b>","Bed Space Availability: ", "</b>", facgeo$What.is.your.current.number.of..Bed.Space.Availability,"<br>",
  # "<b>","Ventilators: ", "</b>", facgeo$How.many.ventilators.do.you.have....numerical.values.only...text,"<br>",
  # "<b>","ICU Beds: ", "</b>", facgeo$What.is.your.current.number.of..ICU.Beds,"<br>",
  
  # "<u>","Length of Time to Operate with Current Supply Chain ", "</u>", "<br>",
    "<u>","Supply Need for Next 8 Weeks", "</u>", "<br>",
  "<b>","Supply Need Concern: " , "</b>", paste(round(facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODED, 0)),"<br>",
  
    
  # "<b>","Current Operational Normalcy | N95 Respirators: " , "</b>", facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..N95.Respirators,"<br>",
  # "<b>","Current Operational Normalcy | Surgical Masks: " , "</b>", facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks,"<br>",
  # "<b>","Current Operational Normalcy | Face Shields/Eye Gear: " , "</b>", facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Face.Shields.Eye.Gear,"<br>",
  # "<b>","Current Operational Normalcy | Gowns: " , "</b>", facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Gowns,"<br>",
  # "<b>","Current Operational Normalcy | Gloves: " , "</b>", facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Gloves,"<br>",
  # 
  # "<u>","Staffing ", "</u>", "<br>",
  # "<b>","Current Situation | Staffing MDs: ", "</b>", facgeo$What.best.describes.your.current.staffing.situations....5.being.most.ready..1.being.least.ready...MD.staff,"<br>",
  # "<b>","Current Situation | Staffing RNs: ", "</b>", facgeo$What.best.describes.your.current.staffing.situations....5.being.most.ready..1.being.least.ready...RN.Staff,"<br>",
  # "<b>","Plans for Expanding Staff: ", "</b>", facgeo$What.are.your.plans.for.expanding.staff.in.the.event.of.a.surge.and.or.workforce.shortage...text,"<br>",
  # 
  # "<u>","Bed Space Availability ", "</u>", "<br>",
  # 
  # "<b>","ICU Beds Situation: ", "</b>", facgeo$What.is.your.space.situation...5.being.most.capable..1.being.least.capable...ICU.Beds,"<br>",
  # "<b>","ICU Beds: ", "</b>", facgeo$What.is.your.current.number.of..ICU.Beds,"<br>",
  # "<b>","NP/Isolation Beds Situation: ", "</b>", facgeo$What.is.your.space.situation...5.being.most.capable..1.being.least.capable...NP.or.Isolation.Beds,"<br>",
  # 
  "<u>","Other Needs ", "</u>", "<br>",
  "<b>","Other Needs: ", "</b>", facgeo$Please.describe.any.other.needs.you.may.have.at.this.time.to.handle.a.potential.surge...text,"</br>", 
  sep = "") %>%
  lapply(htmltools::HTML)


#colour pallette
pal1<-  colorNumeric(palette = "Reds", domain = cdata$totpop, na.color="transparent")



# palcurropnormal<- colorFactor(palette = 'RdYlGn', domain = levels(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks))

#colour pal for cases circl
casespal <- colorFactor(palette = colorRampPalette(c("red", "white")), domain=cdata$totcases,  rev=T)

#colour for bed availability
# palavailability <- colorFactor('RdYlGn', domain = (facgeo$What.is.your.current.number.of..Bed.Space.Availability), rev= F)

# #Concern about supplies for next 8 weeks  cuts ----------------------------------------------------------
facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODEDcut <-
  cut(
    round(facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODED,0),
    c(0, 1, 2, 3, 4, 5), include.lowest = F,
    labels = c(
      "Exhausted all supply options  (1)",
      "No supply chain, reuse, expired products, resource requests  (2)",
      "Difficulty with supply chain  (3)" ,
      "Need resource requests through Local Health Dept. or Gov't  (4)" ,
      "Continuing to procure through regular process  (5)" ))


#colour for faciltiy need concern in next 8 weeks
facneed8pal <- colorFactor(palette = 'RdYlGn', facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODEDcut, rev=F)

##Bed space availability cuts
# facgeo$What.is.your.current.number.of..Bed.Space.Availabilitycut <-
#   cut(
#     facgeo$What.is.your.current.number.of..Bed.Space.Availability,
#     breaks =  quantile(
#       facgeo$What.is.your.current.number.of..Bed.Space.Availability,
#       names = TRUE,
#       type = 4
#     ),
#     # c(round(quantile(facgeo$What.is.your.current.number.of..Patient.Census)[1,1:5])),
#     include.lowest = F
#     # labels = rev(c('0-2 pts',
#     #                '3-7 pts',
#     #                '8-16 pts',
#     #                '17-'))
#   )












##Bed space availability cuts
# facgeo$What.is.your.current.number.of..Bed.Space.Availabilitycut <-
#   cut(
#     facgeo$What.is.your.current.number.of..Bed.Space.Availability,
#     breaks =  quantile(
#       facgeo$What.is.your.current.number.of..Bed.Space.Availability,
#       names = TRUE,
#       type = 4
#     ),
#     # c(round(quantile(facgeo$What.is.your.current.number.of..Patient.Census)[1,1:5])),
#     include.lowest = F
#     # labels = rev(c('0-2 pts',
#     #                '3-7 pts',
#     #                '8-16 pts',
#     #                '17-'))
#   )


#map title
tag.map.title <- tags$style(HTML("
  .leaflet-control.map-title { 
    transform: translate(-50%,20%);
    position: fixed !important;
    left: 30%;
    text-align: center;
    padding-left: 10px; 
    padding-right: 10px; 
    background: rgba(255,255,255,0.75);
    font-weight: bold;
    font-size: 28px;
  }
"))

title <- tags$div(
  tag.map.title, HTML("COVID-19 RESPONSE | QUILOMBOLA COMMUNITY")
)  










```


Column {data-width=450}
-----------------------------------------------------------------------

### Cases + Facilities + Risk

```{r}

leaflet (cdata) %>% 
  setView( -56.59501, -1.246823 , zoom=9) %>% 
  addPolygons(
    data = quil, 
    color = "white",
    weight = 2,
    fillColor ="green",
    fillOpacity = 0,
    opacity = .35,
    highlightOptions = highlightOptions(
      color = "dark grey",
      weight = 3.5,
      opacity = .6,
      bringToFront = F
    ),
    label = cntyinfo,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "13px",
      direction = "auto"),
    group = "<b>Quilombola Community Boundary</b>") %>% 
  
  # addPolygons(
  #   data=brasil, 
  #   group = "<b>Brasil Boundary</b>") %>%
  
  addMarkers(
    data = cdata,
    lng = cdata$x,
    lat = cdata$y,
    # clusterOptions = markerClusterOptions(freezeAtZoom = 4.5),
    # icon = "blue", 
    popup = NULL,
    popupOptions = T,
    label = cntyinfo,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "13px",
      direction = "auto"
    ),
    clusterId =
      "quakesCluster",
    group =  "<b>Brief Summary of Polygon</b>") %>% 
  
  
  # addCircleMarkers(
  #   color = "red", 
  #  lng =  rpts@coords[,1], 
  #  lat= rpts@coords[,2], ##coords
  # 
  #   group="<b>Randomly Selected Locations</b>") %>% 
  
  
  
  
  
  # addCircleMarkers(lng = cdata$x,
  #                  lat= cdata$y,
  #                  data=cdata$cases,
  #   color = "yellow", 
  #   group = "<b>Community Need</b>") %>%


  
  addCircleMarkers(
    data = cdata,
    lng = cdata$x,
    lat = cdata$y,
    color = ~ casespal(cdata$totcases),
    popup = as.character(cdata$totcases),
    radius = ~ sqrt(cdata$totcases) * 1.5,
    #edited the size of circles for cases
    weight = .5,
    label = caseslabel,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "13px",
      direction = "auto"
    ),
    opacity = 0.95,
    # color = ~casespal(pts@data$V3),
    group =     "<b>Cases Per Locality</b>"
  ) %>% 
  

  addLabelOnlyMarkers(
    data = cdata,
    lng = cdata$x,
    lat = cdata$y,
    label =  as.character(cdata$totcases),
    # label = "Label w/ custom CSS style",
    labelOptions = labelOptions(
      noHide = T,
      direction = 'right',
      textOnly = T,  
      style = list(
        "color" = "white",
        # "font-family" = "serif",
        # "font-style" = "italic",
        # "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px"
        # "border-color" = "rgba(0,0,0,0.5)"
      )),
    group= "<b>Cases Per Locality</b>" ) %>%  
  
  
  
  # markers -----------------------------------------------------------------




addMarkers(
  data = facgeo,
  lng = facgeo$lon,
  lat = facgeo$lat,
  # clusterOptions = markerClusterOptions(freezeAtZoom = 4.5),
  icon = NULL,
  popup = NULL,
  popupOptions = T,
  label = facinfo,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "13px",
    direction = "vertical"
  ),
  clusterId = 
    "quakesCluster",
  group =  "<b>Facility Locations w/ Brief Summary</b>"
) %>%
  








# ##operational normalacy current with supplies ---------------------------
# addCircleMarkers(data=facgeo,
#                  lng=facgeo$lon, 
#                  lat = facgeo$lat,
#                  radius = 10,
#                  color = ~palcurropnormal(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..N95.Respirators),
#                  stroke = FALSE, 
#                  fillOpacity = 0.5,
#                  # clusterOptions = markerClusterOptions(freezeAtZoom = 12.5),
#                  group= "Current Operational Normalcy | N95 Respirators") %>% 
  
  
  # addCircleMarkers(data=facgeo,
  #                  lng=facgeo$lon, 
  #                  lat = facgeo$lat,
  #                  radius = 10,
  #                  color = ~palcurropnormal(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks),
  #                  stroke = FALSE, 
  #                  fillOpacity = 0.5,
  #                  # clusterOptions = markerClusterOptions(freezeAtZoom = 12.5),
  #                  group= "Current Operational Normalcy | Surgical Masks") %>% 
  
  
  # addCircleMarkers(data=facgeo,
  #                  lng=facgeo$lon, 
  #                  lat = facgeo$lat,
  #                  radius = 10,
  #                  color = ~palcurropnormal(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Face.Shields.Eye.Gear),
  #                  stroke = FALSE, 
  #                  fillOpacity = 0.5,
  #                  # clusterOptions = markerClusterOptions(freezeAtZoom = 12.5),
  #                  group= "Current Operational Normalcy | Face Shield/Eye Gear") %>% 
  # 
  # addCircleMarkers(data=facgeo,
  #                  lng=facgeo$lon, 
  #                  lat = facgeo$lat,
  #                  radius = 10,
  #                  color = ~palcurropnormal(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Gowns),
  #                  stroke = FALSE, 
  #                  fillOpacity = 0.5,
  #                  # clusterOptions = markerClusterOptions(freezeAtZoom = 12.5),
  #                  group= "Current Operational Normalcy | Gowns") %>% 
  # 
  # 
  # addCircleMarkers(data=facgeo,
  #                  lng=facgeo$lon, 
  #                  lat = facgeo$lat,
  #                  radius = 10,
  #                  color = ~palcurropnormal(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Gloves),
  #                  stroke = FALSE, 
  #                  fillOpacity = 0.5,
  #                  # clusterOptions = markerClusterOptions(freezeAtZoom = 12.5),
  #                  group= "Current Operational Normalcy | Gloves") %>% 
  
  
  
  
  # ##Availability of Supplies ---------------------------


# 
# addLabelOnlyMarkers(
#   data = facgeo,
#   lng = facgeo$lon,
#   lat = facgeo$lat,
#   label =  ~ as.character(facgeo$What.is.your.current.number.of..Bed.Space.Availability),
#   # label = "Label w/ custom CSS style",
#   labelOptions = labelOptions(
#     noHide = T,
#     direction = 'right',
#     textOnly = T,  
#     style = list(
#       "color" = "white",
#       # "font-family" = "serif",
#       # "font-style" = "italic",
#       # "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
#       "font-size" = "12px"
#       # "border-color" = "rgba(0,0,0,0.5)"
#     )),
#   group= "Current Availability | Bed Space"
# ) %>% 
  
  
  
  # addLabelOnlyMarkers(
  #   data = facgeo,
  #   lng = facgeo$lon,
  #   lat = facgeo$lat,
  #   label =  ~ as.character(facgeo$What.is.your.current.number.of..ICU.Beds),
  #   # label = "Label w/ custom CSS style",
  #   labelOptions = labelOptions(
  #     noHide = T,
  #     direction = 'left',
  #     textOnly = T,
  #     style = list(
  #       "color" = "red",
  #       # "font-family" = "serif",
  #       # "font-style" = "italic",
  #       # "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
  #       "font-size" = "12px"
  #       # "border-color" = "rgba(0,0,0,0.5)"
  #     )),
  #   group= "Current Availability | ICU Beds"
  # ) %>%
  
  #################markers for each health facility by colour
  
  addCircleMarkers(
    data = facgeo,
    lat = ~ lat,
    lng = ~ lon,
    color = ~ facneed8pal(
      facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODEDcut
    ),
    # popup = facgeo$Popup,
    radius = ~sqrt(facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODED * 50),
    group = "<b>Facility Supply Need Concern for Next 8 Weeks</b>"
  ) %>%
  
  
  
  
  hideGroup(c(

    
    # "<b>Quilombola Community Boundary</b>",
    # "<b>Brasil Boundary</b>",
    "<b>Brief Summary of Polygon</b>",
    # "<b>Randomly Selected Locations</b>",
    # "<b>Community Need</b>",
    "<b>Cases Per Locality</b>",
    "<b>Facility Locations w/ Brief Summary</b>",
    "<b>Facility Supply Need Concern for Next 8 Weeks</b>"
    # ,"Current Operational Normalcy | N95 Respirators"
    #, "Current Operational Normalcy | Surgical Masks",
    # "Current Operational Normalcy | Face Shield/Eye Gear",
    # "Current Operational Normalcy | Gowns",
    # "Current Operational Normalcy | Gloves",
    # "Current Availability | Bed Space",
    # "Current Availability | ICU Beds"
    )) %>%
  
  
  
  
  
  
  













  
  
  
  
  
  
  





  
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  # addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", attribution = 'Google') %>%
  # # addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=m&hl=en&x={x}&y={y}&z={z}&s=Ga", attribution = 'Google') %>%




  
  
  
  
addScaleBar() %>% 
  

  
  #Legend Population per Locality
  addLegend(
    position = "topleft",
    pal = pal1,
    values = cdata$totpop,
    # labels = ~pal1,
    title = "Population 2018",
    opacity = 0.35,
    group =  "Population 2018 Est. (%)"
  ) %>%
  #legend color for current operational normalcy; N95 Respirators
  # addLegend(
  #   position = 'topleft',
  #   pal = palcurropnormal,
  #   values = levels(facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..N95.Respirators),
  #   title = "<b>Operational Normalcy Given Current Supply: N95 Respirators </b> </br><i>LengthofTime </i> </br>",
  #   opacity = .75,
  #   group =     "Current Operational Normalcy | N95 Respirators"
  # ) %>%
  
  
  # #legend color for current operational normalcy; Surgical Masks
  # addLegend(
  #   position = "topleft",
  #   pal = palcurropnormal,
  #   values = facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks,
  #   title = "<b>Operational Normalcy Given Current Supply: Surgical Masks </b> </br><i>LengthofTime </i> </br>",  
  #   opacity = .75,
  #   group =     "Current Operational Normalcy | Surgical Masks"
  # ) %>% 
  # 
  # 
  # #legend color for current operational normalcy; Face Shields/Eye Gear
  # addLegend(
  #   position = "topleft",
  #   pal = palcurropnormal,
  #   values = facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks,
  #   title = "<b>Operational Normalcy Given Current Supply: Face Shields/Eye Gear </b> </br><i>LengthofTime </i> </br>",  
  #   opacity = .75,
  #   group =     "Current Operational Normalcy | Face Shield/Eye Gear"
  # ) %>% 
  # 
  # 
  # 
  # #legend color for current operational normalcy; Gowns
  # addLegend(
  #   position = "topleft",
  #   pal = palcurropnormal,
  #   values = facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks,
  #   title = "<b>Operational Normalcy Given Current Supply: Gowns </b> </br><i>LengthofTime </i> </br>",  
  #   opacity = .75,
  #   group =     "Current Operational Normalcy | Gowns"
  # ) %>% 
  # 
  # 
  # 
  # 
  # #legend color for current operational normalcy; Gloves
  # addLegend(
  #   position = "topleft",
  #   pal = palcurropnormal,
  #   values = facgeo$How.long.can.you.operate.with.your.current.supply.chain.for.the.following.items..Surgical.Masks,
  #   title = "<b>Operational Normalcy Given Current Supply: Gloves </b> </br><i>LengthofTime </i> </br>",  
  #   opacity = .75,
  #   group =     "Current Operational Normalcy | Gloves"
  # ) %>% 
  # 
  # 
  #legend color for average facility need CONCERN for next 8 weeks
  addLegend(
    position = "bottomright",
    pal = facneed8pal,
    values = facgeo$Please.indicate.supply.NEED.for.the.next.8weeks....5.being.least.concerned..1.being.most.concerned...ALL.SUPPLIES.AVERAGE.CODEDcut,
    title = "<b>Facility Supply Need Concern for Next 8 Weeks </b> </br>  <i>Averaged </i> </br>",
    opacity = .75,
    group = "<b>Facility Supply Need Concern for Next 8 Weeks</b>"
  ) %>% 


addLayersControl(
  overlayGroups = c(
    # "State Park Locations",
    # "State Park 50-Mile Radius Buffer",
    # "LPHU Locations",
    # # "Tribal LPHU Locations",
    # "Satellite Locations",

    "<b>Quilombola Community Boundary</b>",
    # "<b>Brasil Boundary</b>",
    "<b>Brief Summary of Polygon</b>",
    # "<b>Randomly Selected Locations</b>",
    # "<b>Community Need</b>",
    "<b>Cases Per Locality</b>",
    "<b>Facility Locations w/ Brief Summary</b>",
    "<b>Facility Supply Need Concern for Next 8 Weeks</b>"
    # "Current Operational Normalcy | N95 Respirators"
    # ,"Current Operational Normalcy | Surgical Masks",
    # "Current Operational Normalcy | Face Shield/Eye Gear",
    # "Current Operational Normalcy | Gowns",
    # "Current Operational Normalcy | Gloves",
    # "Current Availability | Bed Space",
    # "Current Availability | ICU Beds"
  ),
  options = layersControlOptions(collapsed = T)) %>% 
  ###how to get the layers of the legend to switch when selected
 
  htmlwidgets::onRender("
function(el, x) {

var updateLegend = function () {
    var selectedGroup = document.querySelectorAll('input:checked')[0].nextSibling.innerText.substr(1);

    document.querySelectorAll('.legend').forEach(a => a.hidden=true);
    document.querySelectorAll('.legend').forEach(l => {
      if (l.children[0].children[0].innerText == selectedGroup) l.hidden=false;
    });
};
updateLegend();
this.on('baselayerchange', e => updateLegend());



}") %>% 
  addMiniMap(  toggleDisplay = T, autoToggleDisplay = T, strings = list(hideText = "Hide MiniMap", showText = "Show MiniMap") ,position="bottomleft", zoomLevelOffset=-9,
               tiles = providers$CartoDB.DarkMatter, mapOptions = list()) %>% 
    
  addControl(title, position = "topleft", className="map-title")



```


Column {data-width=150, data-height=350}
-----------------------------------------------------------------------

### Cases Per Locality (Cumulative)



```{r include=FALSE}
dates<-select(data, matches("X2020")) %>% 
  mutate(Nom=as.factor(data$Nom)) %>%
  pivot_longer(
    cols = starts_with("X2020"),
    names_to = "date",
    names_prefix = "X",
    values_to = "rank",
    values_drop_na = TRUE
  ) %>% 
  group_by(date) %>%
  spread(Nom, rank) %>% 
  ungroup() %>% 
  mutate(
    # Nom=as.factor(Nom),
    date=as.Date(date, format= "%Y.%m.%d"))
dates


ay <- list(
  #tickfont = list(color = "red"),
  overlaying = "y",
  side = "right"
)

p <- plot_ly() %>%
  add_trace(x = dates$date, y = cumsum(dates$`Água Fria`), name = "Água Fria",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Alto Trombetas I`), name = "Alto Trombetas I",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Alto Trombetas I2`), name = "Alto Trombetas I2",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Alto Trombetas II`), name = "Alto Trombetas II",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Ariramba`),  name = "Ariramba",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Boa Vista`),  name = "Boa Vista",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Cachoeira Porteira`),  name = "Cachoeira Porteira",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Erepecuru`), name = "Erepecuru",type = "scatter", mode = "markers") %>%
  add_trace(x = dates$date, y = cumsum(dates$`Trombetas`),  name = "Trombetas",type = "scatter", mode = "markers") %>%
  layout(
    title = "Cases Per Locality", yaxis2 = ay,
    xaxis = list(title="Date", ticks=dates$date)
  )
```

```{r echo=FALSE, message=FALSE, warning=FALSE}


p

```

### Notes

```{r}

```

<b>About the Quilombola Community:</b>
</br>A resilient Community in Brasil, responding to challenges of inequality and COVID-19 with strength and courage. 
</br>
</br><b>Purpose of Dashboard:</b>
</br>To provide near real-time information for community and strategic planning.
</br>
</br>
</br><i>Note:</i> data is located [**here**](https://docs.google.com/spreadsheets/d/1kVIMl-XB-QvM1zpP3N5Oi3dAKiShtlC43WjHn3IEjTg/edit?usp=sharing).
</br>
</br>
<b>How to Use Map:</b>
</br>* Click on the map "icons" to display more information.
</br>
</br>* Hover over the map to highlight and display more information. 
</br>
</br>* Toggle "on" and "off" the boxes to reveal auxillary information and  layers in the legend to reveal more information on the map.
</br>
</br>* Zoom in and out using "+" or "-" buttons at the top left of map, or by pressing and holding the "CNTRL" key and scrolling the wheel on your mouse up or down.
</br>
<br>
-----
<br>
</br><b>Data Sources:</b>
</br>* Quilombola Community data.
</br>* [**ARQMO**](http://cpisp.org.br/quilombolas-em-oriximina/quem-sao-como-vivem/arqmo/) Team.
</br>* [**ECAM**](http://ecam.org.br/en/) Team.
</br>
</br>

Updated on `r Sys.Date()`